\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-20 paper.tex
added OP_CHECKSIG to difficulties

%$\bullet$ \texttt{OP\_CHECKSIG} is a bitch to describe.

>>>>

$\bullet$ \texttt{OP\_CHECKSIG} and related op-codes refer to the serialized form of the surrounding transaction. This is important as the signature which \texttt{OP\_CHECKSIG} verifies serves dually to prove that the author of the transaction is in control of the relevant private key (corresponding to the public key which hashes to the address to which the relevant locked bitcoins were spent) and in fact authored the transaction presently under consideration. Due to the complexities of referencing the serialized form the transaction with big-step semantic inference rules, we did not, after much struggle, provide such rules for such op-codes.
